Transform and Tell:\\The News Image Caption Writer That Remembers Rare Names

### 2019-11-05 paper/paper.tex
Update references

Most existing captioning systems can only generate a generic description of an
image \cite{Vinyals2014ShowAT, Fang2014FromCT, Karpathy2015DeepVA,
Rennie2016SelfCriticalST, Lu2016KnowingWT, Anderson2017BottomUpAT}, mainly
because these architectures cannot handle an open vocabulary and early
captioning datasets such as MS COCO \cite{Lin2014MicrosoftCC,
Chen2015MicrosoftCC} and Flickr30k \cite{Young2014FromID} were annotated using
only visual cues present in the image. More recently, datasets such as TIME
\cite{Tariq2017ACE}, BreakingNews \cite{Ramisa2016BreakingNewsAA}, and GoodNews
\cite{Biten2019GoodNews} include real-life captions scraped from online
newspapers. To the best of our knowledge, all existing models that are trained
on these news datasets use template-based methods to insert named entities.

@@

\begin{enumerate}
   \item We introduce the NYTimes+ dataset, containing 446K articles and 794K
   images with captions from the New York Times spanning 14 years. This
   constitutes the largest news image captioning dataset to date. NYTimes+ is
   built upon the GoodNews dataset, but we write a custom parser to collect
   higher-quality articles and metadata such as the location of an image within
   the page.

   \item We build a captioning model that combines the power of transformers,
   byte-pair encoding, and attention over three different modalities (text,
   images, and faces). We show that our model achieves state-of-the-art results
   with a significant margin over previous methods, and in particular, it can
   generate names not seen during training.

@@

Recent image captioning systems are based mostly on ``Show, Attend, Tell"
\cite{Xu2015ShowAA}, which uses a simple hard attention over the image. Later
improvements include giving the model the option to not attend to any image
region \cite{Lu2016KnowingWT}, using reinforcement learning to directly
optimize for the CIDEr metric \cite{Rennie2016SelfCriticalST}, and using a
bottom-up approach to propose a region to attend to
\cite{Anderson2017BottomUpAT}. All of these system generate generic captions.

@@

\section{Dataset}

A summary of the original GoodNews dataset and our new dataset is shown in
Table \ref{tab:datasets}. The GoodNews+ dataset is our attempt at recollecting
the original GoodNews dataset. We managed to crawl all the original articles,
but the number of images is slightly less, either due to dead links or
not crawling images unrelated to the main article. GoodNews+ allows us to make the
following observations about the original GoodNews dataset:

\begin{itemize}
   \item On average, half of the article body is missing. This includes
         the first few paragraphs that might contain important information
         about the top caption.
   \item The dataset contains a small number Spanish articles.
   \item Sometimes images from the recommendation sidebar, which are not part
         of the main article, are included in the dataset.
\end{itemize}

This motivates us to recollect data from the New York Times in a more careful
manner, using our own parser. We call this NYTimes+.

\begin{table}[t]
	\caption {Summary of datasets}
	\label{tab:datasets}
	\centering
	\begin{tabular}{llll}
		\toprule
		  & GoodNews  & GoodNews+ &   NYTimes+ \\
		\midrule
      No of articles & 241 808 & 241 808 & 445 828 \\
      No of images   & 462 642 & 440 112 & 794 085 \\
      Article length & 451 & 963 & 974 \\
      Caption length & 18 & 18 & 18 \\
      Start month & Jan 10 & Jan 10 & Mar 05\\
      End month & Jul 18 & Jul 18 & Sep 19 \\
		\bottomrule
	\end{tabular}
\end{table}

In addition to having a more complete coverage, we also collect information
about the image position in each article. As shown in Figure \ref{fig:dist},
about 40\% of the articles have two or more images.

\begin{figure}[h]
   \begin{center}
   \includegraphics[width=0.8\linewidth]{figures/caption_dist.png}
   \end{center}
      \caption{Distribution of images across articles.}
   \label{fig:dist}
   \end{figure}

@@

We use ResNeXt-101 \cite{Xie2016AggregatedRT} to obtain an embedding for
the images. For each generation step, we use the Scalar-Dot-Product attention
\cite{Vaswani2017AttentionIA} to attend to the image and to article separate.
The two attended representations are then concatenated and fed as input to
the self-attention layer.

>>>>

Most existing captioning systems can only generate a generic description of an
image \cite{Vinyals2015ShowAT, Fang2015FromCT, Karpathy2015DeepVA,
Rennie2017SelfCriticalST, Lu2017KnowingWT, Anderson2017BottomUpAT}, mainly
because these architectures cannot handle an open vocabulary and early
captioning datasets such as MS COCO \cite{Lin2014MicrosoftCC,
Chen2015MicrosoftCC} and Flickr30k \cite{Young2014FromID} were annotated using
only visual cues present in the image. More recently, datasets such as TIME
\cite{Tariq2017ACE}, BreakingNews \cite{Ramisa2016BreakingNewsAA}, and GoodNews
\cite{Biten2019GoodNews} include real-life captions scraped from online
newspapers. To the best of our knowledge, all existing models that are trained
on these news datasets use template-based methods to insert named entities.

@@

\begin{enumerate}
   \item We introduce NYTimes+, the largest news image captioning dataset to
   date, containing 446K articles and 794K images with captions from the New
   York Times spanning 14 years. NYTimes+ is built upon the GoodNews dataset,
   but we write a custom parser to collect higher-quality articles and metadata
   such as the location of an image within the page.

   \item We build a captioning model that combines the power of transformers,
   byte-pair encoding, and attention over three different modalities (text,
   images, and faces). We show that our model achieves state-of-the-art results
   with a significant margin over previous methods, and in particular, it can
   generate names not seen during training without the use of templates.

@@

Recent image captioning systems are based mostly on ``Show, Attend, Tell"
\cite{Xu2015ShowAA}, which uses a simple hard attention over the image. Later
improvements include giving the model the option to not attend to any image
region \cite{Lu2017KnowingWT}, using reinforcement learning to directly
optimize for the CIDEr metric \cite{Rennie2017SelfCriticalST}, and using a
bottom-up approach to propose a region to attend to
\cite{Anderson2017BottomUpAT}. All of these systems generate generic captions.

@@

\section{Datasets}

\begin{table}[t]
	\caption {Summary of datasets}
	\label{tab:datasets}
	\centering
	\begin{tabular}{llll}
		\toprule
		  & GoodNews  & GoodNews+ &   NYTimes+ \\
		\midrule
      No. of articles & 241 808 & 241 808 & 445 828 \\
      No. of images   & 462 642 & 440 112 & 794 085 \\
      Article length & 451 & 963 & 974 \\
      Caption length & 18 & 18 & 18 \\
      Start month & Jan 10 & Jan 10 & Mar 05\\
      End month & Jul 18 & Jul 18 & Sep 19 \\
		\bottomrule
	\end{tabular}
\end{table}

\subsection{GoodNews and GoodNews+}

As a starting point, we use the GoodNews dataset, previously the largest
dataset on news image captioning. As part of the quality check, we also
reconstruct the same dataset on our own. We use the New York Times API and
write a custom parser to recollect and extract all the articles and images in
in the same period as GoodNews from the original source. We call this
GoodNews+. We managed to crawl all the original articles, but the number of
images is slightly less, either due to dead links or not crawling images
unrelated to the main article. GoodNews+ allows us to make the following
observations about the original GoodNews dataset:

\begin{itemize}
   \item The average length of an article in GoodNews is 451 words, while it is
         963 words in GoodNews+. Thus half of the article body is missing in
         GoodNews. This includes the first few paragraphs that might contain
         important information about the top caption. Looking through the
         publicly released code, we found that this is because the original
         parser used by \cite{Biten2019GoodNews} fails to recognize certain
         HTML tags used in New York Times web pages.
   \item GoodNews contains X Spanish articles, adding unwanted noise to the
         training.
   \item GoodNews sometimes include images from the recommendation sidebar,
         which are not part of the main article.
\end{itemize}

Despite the above limitation, we will use the original GoodNews dataset in our
experiments, along with the original train-validation-test split to make
comparison to previous works easier.

\subsection{NYTimes+}

At the same time, we also construct a new dataset, which we call NYTimes+.
NYTimes+ exhibits several advantages over GoodNews:

\begin{itemize}
   \item By increasing the collection period to the last 14 years (March 2005
   -- September 2019), NYTimes+ contains 80\% more articles and images, thus
   becoming the largest news captioning dataset.
   \item NYTimes+ contains only English articles.
   \item We are careful to include only images that are part of the main
   article.
   \item In addition to having a more complete coverage, we also collect
   information about the image position in each article. As shown in Figure
   \ref{fig:dist}, about 40\% of the articles have two or more images.
\end{itemize}

A summary of the datasets is shown in Table \ref{tab:datasets}.

\begin{figure}[t]
   \begin{center}
   \includegraphics[width=0.8\linewidth]{figures/caption_dist.png}
   \end{center}
      \caption{Distribution of images across articles.}
   \label{fig:dist}
   \end{figure}

@@

We use ResNeXt-101 \cite{Xie2017AggregatedRT} to obtain an embedding for
the images. For each generation step, we use the Scalar-Dot-Product attention
\cite{Vaswani2017AttentionIA} to attend to the image and to article separate.
The two attended representations are then concatenated and fed as input to
the self-attention layer.
